DEMZ

### 2023-05-17 DEMZ_xml_agenda.Rmd
MUZBE: final modifications

>>>>

```{r ZKUS TO JESTE JEDNOU}

x <- xml2::read_xml("P:/w4dz/migrace/new-xml/e4g/stm/16788817.xml")
xp <- XML::xmlParse(xml2::read_xml("P:/w4dz/migrace/new-xml/e4g/stm/16788817.xml"))

class(x)  # "xml_document" "xml_node"    
class(xp) # "XMLInternalDocument" "XMLAbstractDocument"

xmlRoot(x) #Error in UseMethod("xmlRoot") : no applicable method for 'xmlRoot' applied to an object of class "c('xml_document', 'xml_node')"
xroot <- xmlRoot(xp) # ok
print(xroot) # ok

struct <- xml_structure(x) # tiskne, ale ulozi prazdny vektor

#find all str nodes
xml2::xml_find_all(x, ".//property[@name='verRealUser']/display") # nefunguje ! Prazdny xml_nodeset..
xml2::xml_find_all(x, ".//LASTMODDATE") # nefunguje ! Prazdny xml_nodeset..
xml2::xml_find_all(x, ".//objectInfo/createDT") # nefunguje ! Prazdny xml_nodeset..
xml2::xml_find_all(x, ".//esez/objectInfo") # nefunguje ! Prazdny xml_nodeset..
xml2::xml_find_all(x, ".//e4gNazov") # nefunguje ! Prazdny xml_nodeset..
xml2::xml_find_all(x, ".//property name=\"owner\"") # nefunguje ! Prazdny xml_nodeset..

xml2::xml_attr(x, objectInfo)

# SEKVENCNI CTENI

x <- xml2::read_xml(paste0(path_sndb, "16788817.xml"))
xp <- XML::xmlParse(xml2::read_xml(paste0(path_sndb, "16788817.xml")))

class(x)  # "xml_document" "xml_node"    
class(xp) # "XMLInternalDocument" "XMLAbstractDocument"

xroot <- xmlRoot(xp) # ok
print(xroot) # ok
